Synthesizing Symmetric Lenses

### 2018-07-01 papers/SymmetricLenses/main.tex

@@

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.
% end overview

@@

These components only make sense for synchronization when they satisfy
round-tripping laws.  This guarantees that if an identity edit is propagated, no
data gets changed.
\begin{equation}
  \tag{\PutRL}
  \frac{\PutRSymOf{(x,c)} = (y,c')}{\PutLSymOf{(y,c')} = (x,c')}
\end{equation}
\begin{equation}
  \tag{\PutLR}
  \frac{\PutLSymOf{(y,c)} = (x,c')}{\PutRSymOf{(x,c')} = (y,c')}
\end{equation}

>>>>

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.

@@

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.
Consider the trivial lens
\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
the disconnect lens, the cost of each side is the entropy of the data format, so
the total cost is $\EntropyOf{\lstinline{emp_salary} } +
\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
imformation than $\EntropyOf{\lstinline{": " . salary}}$, and
\lstinline{emp_row} contains strictly more information than
\EntropyOf{\lstinline{": " . salary}}, so by our metric
\lstinline{single_emp_map} is preferable to the disconnect lens.
% end overview

@@

These components only make sense for synchronization when they satisfy
round-tripping laws.  This guarantees that if an identity edit is propagated, no
data gets changed.
\begin{equation}
  \tag{\PutRL}
  \frac{\PutRSymOf{(x,c)} = (y,c'')}{\PutLSymOf{(y,c')} = (x,c')}
\end{equation}
\begin{equation}
  \tag{\PutLR}
  \frac{\PutLSymOf{(y,c)} = (x,c')}{\PutRSymOf{(x,c')} = (y,c')}
\end{equation}
